Correcting K-correction: dark energy is based on a math error from 1930

### 2025-01-05 paper/dark_energy_corrections.tex
Use a new figure showing the ratio calculation

\title{Correcting K-correction: fixing the time dilation and zero-point terms resolves the Hubble tension and removes evidence for accelerating expansion}

@@

\begin{figure}
  \includegraphics[width=.75\linewidth]{K-corrections_for_photon_counts.png}
  \caption{An example of how K-correction takes an observed magnitude and
  produce a rest frame magnitude. In this example, $z=1$. The observation
  filter measures magnitude, which is equivalent to measuring the number of
  photons per nanometer. In the bottom left panel, a correction of $1+z$ is
  applied which doubles the photons per nanometer. The top right panel shows
  the effect of correcting for the spectral bandwidth stretching effect --
  correcting all wavelengths for the rest frame means that the measured
  wavelengths have blueshifted, ideally into the cross band $B$ filter. Applying
  both effects, shown in the bottom right panel, requires applying two
  correction factors of $1+z$. This example omits the correction for a similar
  effect related to lower energy due to the Planck relation because CCD cameras
  obviate the need to correct for this effect.
  }
  \label{fig:k-example}
\end{figure}

>>>>

\title{Correcting K-correction: dark energy is based on a math error from 1930}

@@

\begin{figure}
  \includegraphics[width=.75\linewidth, height=0.75\vsize]{k_equation_flow.png}
  \caption{The ratio $K'_{xy}$ is the crux of the K-correction algorithm. We
  are able to observe a SnIa in the redshifted observation frame, but we want
  to compute the magnitude in the rest frame as if no redshift has occurred.
  This computation starts with $F(\lambda$, the spectral energy density that
  describes the expected luminosity in the rest frame. Using the SED, we can
  compute the photon density $F'(\lambda)$ for the rest frame. We show the
  process of computing $R'(\lambda$, the photon density in the observation
  frame, in three phases starting at the top right of the figure. First we
  stretch the photon density, but this step inflates counts. In the second
  step, we correct for the inflated counts by multiplying by $\frac{1}{1+z}$;
  at this point, the total count equals the total count of $F'(\lambda)$.
  Finally, in the third step we finish calculating the observation frame photon
  density $R'(\lambda)$ by accounting for time dilation, which also reduces
  photon counts by a factor of $\frac{1}{1+z}$.  Given the rest frame and
  observation frame photon densities, we can compute the expected ratio of
  photons by totalling the area under the curves in the two panels at the
  bottom of the graph. This example does not show the process of converting
  photon flux to magnitude, nor does it address the zero-point correction.
  }
  \label{fig:k-example}
\end{figure}
